The Countercyclical Component of Capital Regulation

### 2020-04-15 Analysis/Draft/Draft_bookdown.Rmd
Add text on skewness to draft

Table \ref{tab:moments_contribution} also shows that, in line with the theoretical framework, an increase in PD variance is positively associated with *Capital savings* for all portfolios. And in line with the evidence from Tables \ref{tab:main} and \ref{tab:alt}, Panel B in table \ref{tab:moments_cyclicality} shows that the effect of the business cycle on the PD variance is concentrated on corporate portfolios. In sum, the estimated coefficients of the average PD and the PD variance in Table \ref{tab:moments_contribution} and panels A and B in Table \ref{tab:moments_cyclicality} provide strong empirical support to the theoretical framework presented in section 4.1.

At the same time, however, using only the evidence provided by the average and variance of the PD distribution, the hypothesis that portfolio reallocation does not impact *Capital savings* cannot be refuted exactly because the estimated effect of these two moments on *Capital savings* are strongly in line with a model without any portfolio reallocation. Consider now a negative shock to a continuous PD distribution, such that we can measure its skewness and kurtosis. It is trivial that the equivalent scenario of panel A of figure \ref{fig:pdmapcases} wouldn't affect either of these moments. On the other hand, in the second scenario the PD distribution should become more skewed to the right. Even if we think that some assets will become safer during bad times, it is reasonable to expect a larger effect on the right tail than on the left tail of the PD distribution. Consequently, considering a static portfolio, we expect the skewness of the PD distribution to be negatively associated with the GDP growth rate.

Panel C in table \ref{tab:moments_cyclicality} provides evidence that the observed relationship of PD distribution skewness and the business cycle can only be explained with a within portfolion reallocation.

@@

reg.list <- list()
# Run the models
for(i in dep.vars){
formula.text <- formula(paste0("log.RWA.r", i, "_gr ~ mean + var + skew + kurt  | year + bvdid | 0 | Country "))
 data = rename(bank.data.win,
               mean    = paste0("mean.PD"  , i, "_gr"),
               var     = paste0("var.PD"   , i, "_gr"),
               skew    = paste0("skew.PD"  , i, "_gr"),
               kurt    = paste0("kurt.PD"  , i, "_gr"))%>%
   felm(data = ., formula = formula.text ) -> reg.list[[i]]
  }

>>>>

Table \ref{tab:moments_contribution} also shows that, in line with the theoretical framework, an increase in PD variance is positively associated with *Capital savings* for all portfolios. And in line with the evidence from Tables \ref{tab:main} and \ref{tab:alt}, panel B in Table \ref{tab:moments_cyclicality} shows that the effect of the business cycle on the PD variance is concentrated on corporate portfolios. In sum, the estimated coefficients of the average PD and the PD variance in Table \ref{tab:moments_contribution} and panels A and B in Table \ref{tab:moments_cyclicality} provide strong empirical support to the theoretical framework presented in section 4.1.

At the same time, however, using only the evidence provided by the average and variance of the PD distribution, the hypothesis that portfolio reallocation does not impact *Capital savings* cannot be refuted, exactly because the estimated effect of these two moments on *Capital savings* are strongly aligned with the theoretical framework which portfolio reallocation is not present. Consider now a negative shock to a continuous PD distribution, such that we can measure its skewness and kurtosis. It is trivial that the equivalent case with a continuous PD distribution to the scenario in panel A of figure \ref{fig:pdmapcases} wouldn't affect either of these moments. On the other hand, in the second scenario the PD distribution should become more skewed to the right. Even if we think that some assets will become safer during bad times, it is reasonable to expect a larger effect on the right tail than on the left tail of the PD distribution. Consequently, without portfolio reallocation, we should expect the skewness of the PD distribution to be negatively associated with the GDP growth rate.

Panel C in table \ref{tab:moments_cyclicality} provides evidence that the observed relationship between PD distribution skewness and the business cycle cannot be explained without portfolion reallocation. All the statistical significant coefficients are positive, contrary to the expectation if banks wouldn't reallocate their portfolio. Considering an economic downturn, the positive coefficients suggest that banks fight the deterioration of their portfolio credit quality by reducing risk taking in new loans. The combination of these two movements, higher PD of existing exposure and lower PD of new assets, results in a less skewed PD distribution during recessions.

Table \ref{tab:moments_contribution} shows that lower skewness translates to higher *Capital savings*. The effect is statistical significant for all except sovereign portfolios. According to column 1, an increase of 0.182 percentage points in PD distribution skewness growth rate (one standard deviation) decreases total *Capital savings* growth rate by 0.009 percentage points on average, representing 20% of total *Capital savings* standard deviation. The effect is even stronger on corporate portfolios accounting for 40% of their *Capital savings* standard deviation.

@@

reg.list <- list()
# Run the models
for(i in dep.vars){
formula.text <- formula(paste0("log.RWA.r", i, "_gr ~ mean + var + skew   | year + bvdid | 0 | Country "))
 data = rename(bank.data.win,
               mean    = paste0("mean.PD"  , i, "_gr"),
               var     = paste0("var.PD"   , i, "_gr"),
               skew    = paste0("skew.PD"  , i, "_gr"))%>%
   felm(data = ., formula = formula.text ) -> reg.list[[i]]
  }
